---
title: "534_project_notebook"
author: "NL"
date: "22/01/2020"
output: html_document
---

## Jan 22, 2020 API Selection
Reviewed different APIs, discussed with Jasmine and Chris and chose the Github Events API. 

## Jan 23, 2020 Create R wrapper
Took the online mini course "An Introduction to APIs" https://zapier.com/learn/apis/ and read "Best practices for API packages"  https://httr.r-lib.org/articles/api-packages.html. 

Created R wrapper to access repository events https://developer.github.com/v3/activity/events/#list-repository-events. 

```{r, echo=FALSE }
get_repo_log("nganlyle", "534_project", "2020-01-23")
```

## Jan 24, 2020 Create gitevents package
Created the R package and added the file with R wrapper function to the /R package. 

```{r, echo=FALSE }
get_repo_log("nganlyle", "534_project", "2020-01-24")
```

## Jan 25, 2020 Create DF function
Added a function to create a DF to repo_events file using the parsed data that we get from the get_repo_events function. This is probably a more useable format. 

```{r, echo=FALSE }
get_repo_log("nganlyle", "534_project", "2020-01-25")
```

## Jan 26, 2020 Create labbook stamp function
Added a function to print out events for a repo for a given date. 

```{r, echo=FALSE }
get_repo_log("nganlyle", "534_project", "2020-01-26")
```

## Jan 31, 2020 Documentation and testing
Started unit testing using testthat() on my functions. Also updated DESCRIPTION, LICENSE, manual with help files for my functions, NAMESPACE. Created a skeleton README file. 

```{r, echo=FALSE }
get_repo_log("nganlyle", "534_project", "2020-01-31")
```
